---
title: "Final project - Developing Data Products. Course 9 of Data Science in Coursera"
author: "Manuela Escobar"
date: "October/29/2020"
output:
  slidy_presentation: default
  ioslides_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Instructions
This peer assessed assignment has two parts. First, you will create a Shiny application and deploy it on Rstudio's servers. Second, you will use Slidify or Rstudio Presenter to prepare a reproducible pitch presentation about your application.

## Data election
I selected the infert data available in R, it relates to infertility after Spontaneous and Induced Abortion
```{r echo=TRUE}
head(infert)
dim(infert)
class(infert)
```

## Exploratory analysis of my data
The data set contains 8 variables -i.e., education, age, parity, induced, case, spontaneous, stratum, pooled.stratum-. I will include age, parities, induced, and spontaneous in my plot. 

```{r cars, echo = TRUE}
summary(infert)
```

## Interactive plot of my data

I create an interactive plot and predict parities based on woman age.

If you want to use, you may:
- Open the link below
- Slide the woman age for what you want to see the predictions 
- Select in the check box the prediction that you want to see, "Number of predicted parities" or "Number of predicted induced and spontaneous abortions"
- Now you can view the predictions!

In the following link you can find my interactive plot: https://manuelaescobar.shinyapps.io/FinalProject/

And, in this the source code: 
https://github.com/manuelaescobar/Developing_Data_Products
